\documentclass{article}
% A4 Paper setting locked in
\usepackage[a4paper, total={6in, 8in}]{geometry}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{secrets-loader.tex}
\ifdefined\pdfglyphtounicode
  \input{glyphtounicode}
\fi

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\footskip}{6pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated PDF is machine readable/ATS parsable when supported
\ifdefined\pdfgentounicode
  \pdfgentounicode=1
\fi

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{center}
    {\Large\scshape William Bradshaw}  \\ \vspace{1pt}
    \small \Secret{phone}  $|$ \href{mailto:\Secret{email}}{\underline{\Secret{email}}}  $|$
    \href{https://linkedin.com/in/wra-bradshaw}{\underline{linkedin.com/in/wra-bradshaw}}  $|$
    \href{https://github.com/wra-bradshaw}{\underline{github.com/wra-bradshaw}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Melbourne}{Melbourne, Victoria, Australia}
      {Bachelor of Science, Computing and Software Systems}{Mar 2025 -- Nov 2027}
      \resumeItemListStart
        \resumeItem{Relevant Coursework: Object-Oriented Software Development, Design of Algorithms, Calculus 1 \& 2, Linear Algebra.}
      \resumeItemListEnd

    \resumeSubheading
      {Amazon Web Services Training and Certification}{Hobart, Tasmania, Australia}
      {AWS Certified Developer Associate}{Oct 2024 -- Oct 2027}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Junior Software Developer}{March 2024 -- February 2025}
      {Ionata Digital}{Hobart, Tasmania}
      \resumeItemListStart
        \resumeItem{Led the technical delivery of palawahub.com.au, portarthur.org.au, and the 2024 Ionata Christmas Game.}
        \resumeItem{Authored code to resolve bugs and performance issues, maintaining documentation for software development procedures.}
        \resumeItem{Managed technical communication with various stakeholders, translating non-technical client requirements into specific software updates.}
        \resumeItem{Developed and executed manual pre-production testing to catch edge cases, ensuring high-quality, stable software prior to final handover.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Pingbot Redux} $|$ \emph{Developer} $|$ Website}{2024}
          \resumeItemListStart
            \resumeItem{Built a serverless backend on AWS using \textbf{Go} and Lambda, interfaced through API Gateway and DynamoDB.}
            \resumeItem{Applied \textbf{Infrastructure-as-Code (IaC)} principles using \textbf{Terraform} to provision cloud architecture, deploying the entire application across various AWS services.}
            \resumeItem{Developed an interactive 3D web application using Three.js, React Three Fiber, and React.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{diagram-creator \& ai-browser-api} $|$ \emph{Maintainer} $|$ GitHub}{Dec 2025 -- Present}
          \resumeItemListStart
            \resumeItem{Building an automated tool using \textbf{AI} to generate scientific and technical diagrams, exploring smart ways to boost workflow efficiency.}
            \resumeItem{Developing a secure browser extension with a client-side ``Bring Your Own Key'' (BYOK) architecture to safely interface with AI models.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{numberconverter} $|$ \emph{Maintainer} $|$ GitHub}{March 2024}
          \resumeItemListStart
            \resumeItem{Built a zero-dependency \textbf{Go} package to convert between integer values and their English word representations, demonstrating strong fundamental programming concepts.}
            \resumeItem{Wrote generic integer parsing and regex-based string replacement methods to handle arbitrary text formatting.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{nix-darwin \& home-manager} $|$ \emph{Contributor} $|$ GitHub}{Aug 2024 -- Present}
          \resumeItemListStart
            \resumeItem{Collaborated via \textbf{Git} version control to resolve a complex race condition in launchd services through a project-wide codebase cleanup.}
            \resumeItem{Wrote the colima.nix module and updated docker-cli.nix for system-level environment management.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{typst-wasm \& tsdown-plugin-worker} $|$ \emph{Maintainer} $|$ GitHub}{Feb 2026 -- Present}
          \resumeItemListStart
            \resumeItem{Built a WebAssembly (WASM) library to compile Typst code.}
            \resumeItem{Maintained an open-source bundler plugin to support web workers for browser multithreading.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{noise} $|$ \emph{Maintainer} $|$ GitHub}{2024}
          \resumeItemListStart
            \resumeItem{Built a terminal UI application in Rust to generate and shape continuous white noise using a 15-band equalizer.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------EXTRACURRICULAR & LEADERSHIP-----------
\section{Extracurricular \& Leadership}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Projects Officer}{March 2026 -- Present}
      {CISSA (Computing and Information Systems Students Association)}{Melbourne, VIC}
    \resumeSubheading
      {IT Officer}{March 2026 -- Present}
      {MISC (University of Melbourne Information Security Club)}{Melbourne, VIC}
    \resumeItemListStart
        \resumeItem{Triaged and fixed flickering navigation issues on the club website.}
        \resumeItem{Diagnosed and resolved website rendering issues affecting iPhones in lockdown mode.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Go, Python, Java, TypeScript, C, PHP, Nix} \\
     \textbf{Concepts \& Tools}{: Object-Oriented Programming (OOP), Git Version Control, Software Testing Principles, Cloud Architecture, Infrastructure-as-Code (IaC), DevOps, Low-Latency/Performance Optimization (WASM)} \\
     \textbf{Frameworks \& Cloud}{: Amazon Web Services (AWS), Terraform, React}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
